
# Questions

1. How have country rankings shifted over time?

2. What is the distribution of participation by gender? What's the distribution of top scores?

3. How does team size or team composition (e.g., number of first-time participants vs. veterans) relate to overall country performance?

# Load Data
```{r}
library(tidyverse)
```


```{r}
# Option 1: tidytuesdayR package 
install.packages("tidytuesdayR")

tuesdata <- tidytuesdayR::tt_load('2024-09-24')

country_results_df <- tuesdata$country_results_df
individual_results_df <- tuesdata$individual_results_df
timeline_df <- tuesdata$timeline_df
```

Alternative way to load in data using link from github
```{r eval = FALSE}
# Option 2: Read directly from GitHub

country_results_df <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2024/2024-09-24/country_results_df.csv')
individual_results_df <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2024/2024-09-24/individual_results_df.csv')
timeline_df <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2024/2024-09-24/timeline_df.csv')
```

# Explore Data 

How many medals each country has gotten?
```{r}
medals <- country_results_df %>% 
  select(year, country, awards_gold, awards_silver, awards_bronze) %>% 
  mutate(total = awards_gold + awards_silver + awards_bronze) %>%  # create total column
  group_by(country) %>% 
  summarize(all = sum(total), 
            gold = sum(awards_gold),
            silver = sum(awards_silver),
            bronze = sum(awards_bronze)) %>% 
  arrange(-all)

year_country <- country_results_df %>% 
  select(year, country, awards_gold, awards_silver, awards_bronze) %>% 
  mutate(total = awards_gold + awards_silver + awards_bronze) %>% 
  pivot_wider(names_from = country,
              values_from = c(total, awards_gold, awards_silver, awards_bronze))
```


```{r}
ggplot(data = medals %>% 
         head(10), 
       aes(x = country, y = gold)) +
  geom_col() +
  theme_classic()

ggplot(data = medals %>% 
         head(10), 
       aes(x = country, y = silver)) +
  geom_col() +
  theme_classic()
```



